---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Vignette - tonypack

<!-- badges: start -->
<!-- badges: end -->

The goal of tonypack is store Tony's functions created as part of STAT 545B assignments, and possibly for after the course as well.

## Installation

You can install the released version of tonypack from [CRAN](https://CRAN.R-project.org) with:

```{r}
devtools::install_github("tzhang1268/tonypack")
```

## Example

This is a basic example which shows you how to solve a common problem:

If you have a date and want to determine what is the number of days to New Years, using the days_to_ny() function to calculate it.

```{r example}
library(tonypack)

## example of using the days_to_ny function
days_to_ny(lubridate::ymd("2020-10-22"))
```

## Details on the development of each component of the R package

Prior to any steps, first we need to add the devtools library.
```{r}
library(devtools)
```

### Creating the basic R package folder directory

This code section creates the R package folder directory at the specified location. All of the basic necessary files and folders within automatically.
```{r}
create_package("C:/Users/TONY/Desktop/tonypack")
```

### Creating a git reposition locally

This code section set up the git repository locally on the computer. It will require an additional confirmation to confirm the initial commit.
```{r}
use_git()
```
### Creating functions in the R function directory with appropriate function documentation

The following code block created the file which contains my function days_to_ny(). The code can then be added within the R file.
```{r}
use_r("days_to_ny")
```

The roxygen2 library need to be added to create function documentation. Then the basic roxygen2 documentation skeleton can be added via Rstudio user interface. The roxygen2 skeleton is then manually modified. 
```{r}
library(roxygen2)
```

The function documentations  need to be rendered using the following code block. This information can then be accessed by the user when they use the ?function command.
```{r}
document()
```

### Updating the basic documentation and creating the license

The DESCRIPTION file created by create_package() earlier contains the basic information about the R package. The personal information and package information within need to be manually updated. Creating the license uses the following code, which creates license files in the R package.
```{r}
use_mit_license("Tony Zhang")
```

### Creating a test directory

The following code block creates a folder directory for function tests.
```{r}
use_testthat()
```


The following code creates an individual test file for a function. The testing code can then be added into the R file.
```{r}
use_test("days_to_ny")
```

### Creating additional documentation and useful information

This code block creates the README file, which contains overall package information and higher level details.
```{r}
use_readme_rmd()
```

Once the README is updated, use the following code to build it in the package.
```{r}
# Note: I commented this part out because it was not allowing the knit to complete properly. 
# build_readme()
```

Vignettes can be created using the following code block.
```{r}
use_vignette("days_to_ny")
```

Once a vignette is updated, use the following code to build it in the package.
```{r}
build_vignettes()
```
